Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration

### 2022-05-08 manuscript_covid19dashboard.tex
Updated paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Interactive dashboard to monitor the COVID-19 outbreak},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Interactive dashboard to monitor the COVID-19 outbreak}
\author{}
\date{\vspace{-2.5em}}

@@

As of September 20th, 2021, 221 countries and territories are infected
by the COVID-19 worldwide pandemic. Dashboards are the most often used
visualization method for visualizing COVID-19 data and informing the
public. The main objective of this study is to identify different
features, visualization methods \& improvements that should be occurred
by exploring the existing dashboards and to develop a dashbored to
visualize COVID-19 outbreak in Sri Lanka. We explored 15 different
dashboards. The most commonly used visualization methods in dashboard
development are bar charts, line charts, and interactive maps.
Dashboards that fit on a single screen are preferable than others.

@@

Initially 15 dashboards were compared to determine which data types are
most frequently shown in dashboards. The 15 dashboards we used in the
study are listed below (Table 1).

@@

\hypertarget{summary-of-data-representation-on-dashboards}{%
\subsection{Summary of data representation on
dashboards}\label{summary-of-data-representation-on-dashboards}}

@@

\hypertarget{software}{%
\subsection{Software}\label{software}}

R software was used for data cleaning and analysis. The flexdashboard
(Iannone, Allaire, and Borges 2020) package was used to build the data
visualization dashboard. The initial layout for the dashboard was
prepared based on Krispin (2021).

\hypertarget{data-visualization}{%
\subsection{Data visualization}\label{data-visualization}}

In this study, we have daily COVID-19 data related to deaths, recovered
and confirmed cases in all 25 districts in Sri Lanka. This structure
generates a multiple time series collection. Visualizing these time
series data is useful to identify similarities and dissimilarities
between districts and their general trends. There are two approaches to
visualizing these time series: (i) drawing individual time series plots
for each district, and (ii) simultaneously plots all time series on a
single panel. Plotting separate panels for each district is not
effective. The reason is that it is hard to compare across 25 different
panels at once. Plotting all time series simultaneously is also not
possible due to overlapping time series and scale differences. We use
heatmaps ~to visualize global and local similarities and dissimilarities
across districts (Peng (2008)) along with Tree Maps, Choropleth Maps,
and ~Dorling Cartogram. The cumulative number of confirmed deaths, and
confirmed cases (both on log scale and linear scale) were used to
compare the status of Sri Lanka against the top-10 countries affected by
COVID-19. Furthermore, we use color-blind friendly colour palettes for
the graphics. To represent qualitative data, a diverging colour palette
was used, and to represent numeric variables, a sequential colour theme
was used. Table 5 provides an overview of methods that have been used to
visualize data.

@@

@@

The ``Sri Lanka COVID-19 Dashboard'' provides an overview of the
COVID-19 pandemic for Sri Lanka. This dashboard has eight panels as
follows.

@@

Inorder, to compare patterns across districts min-max transformation is
used to normalize data into 0-1 scale.

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Distribution of COVID19 Cases by Districts Plotted on a Single
Panel}
\end{figure}

@@

\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

Bar charts \& line charts are the most frequently used tools for the
visualization of total cases, daily cases \& comparisons with respect to
time. Some dashboards contained doughnut shape pie charts to summarize
the total figures. In almost each and every dashboard, value boxes have
been used to represent total figures. Some dashboards contained
interactive maps \& data tables to visualize the distribution of cases
by country, province, region or state. All dashboards are daily updating
real time dashboards. Gender, age groups and ethnicity can be identified
as common breakdowns. The data sets \& related links are available on
most of the dashboards \& can be downloaded. It can be seen that it is
very easy, clear and user friendly to identify confirmed, recovered and
deceased cases in dashboards which include one color theme for the whole
dashboard. Dashboards with the dark background are more comfortable to
the eyes than dashboards with light background \& light colors. Also, it
is better if the dashboard can be fitted on a single screen rather than
adjusting through a grid overlay.

@@

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/1} \caption{Johns Hopkins University COVID-19 Dashboard}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/2} \caption{WHO COVID-19 Dashboard}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/3} \caption{COVID-19 Surveillance Dashboard}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.39in]{Images/4} \caption{Corona cases per Municipality in Belgium Dashboard}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/5} \caption{COVID-19 dashboard for England}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/6} \caption{New Zealand COVID-19 Dashboard}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/7} \caption{COVID-19 Dashboard for Pakistan}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/8} \caption{COVID-19 in Canada dashboard}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/9} \caption{India COVID-19 Dashboard}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.12in]{Images/10} \caption{Italy COVID-19 Dashboard}\label{fig:unnamed-chunk-15}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/11} \caption{Jamaica COVID-19 Dashboard}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.25in]{Images/12} \caption{GCI COVID-19 Dashboard for Russia}\label{fig:unnamed-chunk-17}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.4in]{Images/13} \caption{COVID-19 Live Situational Analysis Dashboard of Sri Lanka}\label{fig:unnamed-chunk-18}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/14} \caption{COVID 19 ZA South Africa Dashboard}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/15} \caption{Robert Koch-Institute COVID-19 dashboard for German}\label{fig:unnamed-chunk-20}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Interactive dashboard to monitor the COVID-19 outbreak and
Vaccine Administration}
\author{}
\date{\vspace{-2.5em}}

@@

As of September 20th, 2021, 221 countries and territories are infected
by the COVID-19 worldwide pandemic. Dashboards are the most often used
visualization method for visualizing COVID-19 data and informing the
public. We explored 15 different dashboards.

@@

Dashboards are one of the best visual interpretation method of tracking
the spread \& communication of COVID-19 pandemic. Initially 15
dashboards were compared to determine which data types are most
frequently shown in dashboards. The 15 dashboards we used in the study
are listed below (Table 1). We compared dashboards to identify the
different features, visualization methods and improvements that should
be occurred.

@@

First, dashboards were compared to determine which data types are most
frequently shown in dashboards. The results are shown in Table 02.

@@

\hypertarget{design-and-development}{%
\subsection{Design and development}\label{design-and-development}}

R software was used for data cleaning and analysis. The flexdashboard
(Iannone, Allaire, and Borges 2020) package was used to build the data
visualization dashboard. The initial layout for the dashboard was
prepared based on Krispin (2021). Data visualizations are generated
using ggplot2 (\textbf{ggplot2?}) and plotly (Sievert 2020) packages in
R. we used color-blind friendly colour palettes for the graphics. To
represent qualitative data, a diverging colour palette was used, and to
represent numeric variables, a sequential colour theme was used. Table 5
provides an overview of methods that have been used to visualize data.

@@

The source code to reprouduce the results are available in a public
GitHub repository and can be access online via
\url{https://github.com/thiyangt/covid19srilanka}

@@

The ``Sri Lanka COVID-19 Dashboard'' provides an overview of the
COVID-19 pandemic and administration of vaacine information in Sri
Lanka. Figure 1 shows an screenshot of the dashboard. This dashboard has
eight panels as listed in Table 6. The deployed dashboard is made
accessible to public through
\url{https://thiyanga.netlify.app/post/covid19srilankadb/}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{images/dashboard}

}

\caption{Overview Panel: Screeshot of the Dashboard}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Distribution of COVID19 Cases by Districts: (A) Plotted on a
Single Panel, (B) Plotted on Separate Panels.}
\end{figure}

@@

We now describe the novel visualization approaches we included in out
dashboard. To effectively distribute the vaccine and to support
situational awareness and inform policy makers decision making it is
important to know the district-wise spread of COVID-19 cases. We have
daily COVID-19 data related to confirmed cases in all 25 districts in
Sri Lanka. This structure generates a multiple time series collection.
Visualizing these time series data is useful to identify similarities
and dissimilarities between districts and their general trends. There
are two approaches to visualizing these time series: (i) drawing
individual time series plots for each district (as shown in Figure 2),
and (ii) simultaneously plots all time series on a single panel (as
shown in Figure 3). Plotting all time series simultaneously is also not
possible due to overlapping time series and scale differences. Plotting
separate panels for each district is not effective. The reason is that
it is hard to compare across 25 different panels at once. In order to
overcome these problems in multiple time series visualization, we use
heat maps ((Peng (2008))) to visualize global and local similarities and
dissimilarities across districts. The associated results are shown in
Figure 3. Here two heatmaps are used to show the global variations
(Figure 3: A) and local variation (Figure 3: B) in the time series
collection. Figure 3-A cell colours represent the actual counts of the
COVID-19 confirmed cases. This is useful to get an idea about the
differences in absolute values. Figure 3-B cell colours represent the
normalized values created applying the min-max transformation. Min-max
transformation is applied to each district time series by using the
corresponding district minimum and maximum value of the time series.
This helps us to get an idea about patterns within districts. For
example, according to Figure 3A we can see Colombo, Gampaha and Kalutara
districs COVID-19 cases are significantly higher than other districts.
According to Figure 3B all districts show an increasing trend pattern as
the right-hand side of the cells are lighter than the left-hand side
cells in the heat map. Furthermore according to Figure 3B all districts
reported high number of cases on 19, 24, 29 August, 2021. Figure 3B is
useful for identifying these local outlying behaviours. As shown in
Figure 4, we also use Choropleth map and Dorling cartogram to visualize
spatial distribution of COVID-19 cases. The vaccination information are
visualize through interactive time series plots and bar charts. A
screenshot of associated panels are shown in Figure 5 and Figure 6.

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Spatial DIstribution of COVID1-19 Cases by Districts}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/d3}

}

\caption{Time Series Plot of Distribution of First Dose and Second Dose}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/d2}

}

\caption{Distribution of Vaccines by Different Types and Dose}\label{fig:unnamed-chunk-7}
\end{figure}

@@

Bar charts and line charts are the most frequently used tools for the
visualization of total cases, daily cases and comparisons with respect
to time. Some dashboards contained doughnut shape pie charts to
summarize the total figures. In almost each and every dashboard, value
boxes have been used to represent total figures. Some dashboards
contained interactive maps \& data tables to visualize the distribution
of cases by country, province, region or state. All dashboards are daily
updating real time dashboards. Gender, age groups and ethnicity can be
identified as common breakdowns. The data sets \& related links are
available on most of the dashboards \& can be downloaded. It can be seen
that it is very easy, clear and user friendly to identify confirmed,
recovered and deceased cases in dashboards which include one color theme
for the whole dashboard. Dashboards with the dark background are more
comfortable to the eyes than dashboards with light background \& light
colors. Also, it is better if the dashboard can be fitted on a single
screen rather than adjusting through a grid overlay.

@@

\leavevmode\hypertarget{ref-plotly}{}%
Sievert, Carson. 2020. \emph{Interactive Web-Based Data Visualization
with r, Plotly, and Shiny}. Chapman; Hall/CRC.
\url{https://plotly-r.com}.

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/1} \caption{Johns Hopkins University COVID-19 Dashboard}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/2} \caption{WHO COVID-19 Dashboard}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/3} \caption{COVID-19 Surveillance Dashboard}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.39in]{Images/4} \caption{Corona cases per Municipality in Belgium Dashboard}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/5} \caption{COVID-19 dashboard for England}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/6} \caption{New Zealand COVID-19 Dashboard}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/7} \caption{COVID-19 Dashboard for Pakistan}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/8} \caption{COVID-19 in Canada dashboard}\label{fig:unnamed-chunk-15}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/9} \caption{India COVID-19 Dashboard}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.12in]{Images/10} \caption{Italy COVID-19 Dashboard}\label{fig:unnamed-chunk-17}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/11} \caption{Jamaica COVID-19 Dashboard}\label{fig:unnamed-chunk-18}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.25in]{Images/12} \caption{GCI COVID-19 Dashboard for Russia}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.4in]{Images/13} \caption{COVID-19 Live Situational Analysis Dashboard of Sri Lanka}\label{fig:unnamed-chunk-20}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/14} \caption{COVID 19 ZA South Africa Dashboard}\label{fig:unnamed-chunk-21}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/15} \caption{Robert Koch-Institute COVID-19 dashboard for German}\label{fig:unnamed-chunk-22}
\end{figure}
